Fast Sorting on Modern Computers

### 2005-08-14 docs/tech_report/shell.tex
finished \cc vs \n search

Shellsort is a derivative of insertion sort designed to offer a compromise
between the performance of mergesort and radixsort, and the space efficiency of
selection sort, bubblesort and insertion sort. It was designed by Donald Shell
in 1959, and described in \cite{Shell59}\footnote{Shell describes the former
sorts as ``Merging Pairs'' and ``floating decimal sort'', respectively, and the
latter sorts as ``finding the smallest'', ``interchanging pairs'' and ``sifting'',
respectively.}.

@@

Two versions of Gonnet's sort were used. The first was taken directly from the
code presented by Sedgewick, and only slightly modified to fit into the
framework used.  The second was modified to reduce the complexity of the loop
bounds, and to remove a sentinel check in the inner loop. Code for
\cc{shellsort} and \cc{improved\_shellsort} is shown in Figures \ref{Shellsort
code} and \ref{Improved Shellsort code}.

>>>>

Shellsort is a derivative of insertion sort designed to offer a compromise
between the performance of mergesort and radixsort, and the space efficiency of
selection sort, bubblesort and insertion sort. It was designed by Donald Shell
in 1959, and described in \cite{Shell59}\footnote{Shell describes the former
sorts as \n{Merging Pairs} and \n{Floating Decimal Sort}, respectively, and the
latter sorts as \n{Finding the Smallest}, \n{Interchanging Pairs} and
\n{Sifting}, respectively.}.

@@

Two versions of Gonnet's sort were used. The first was taken directly from the
code presented by Sedgewick, and only slightly modified to fit into the
framework used.  The second was modified to reduce the complexity of the loop
bounds, and to remove a sentinel check in the inner loop. Code for shellsort and
improved shellsort is shown in Figures \ref{Shellsort code} and \ref{Improved
Shellsort code}.
